Misspecification Demonstration

### 2022-07-27 misspecification_study/misspec_demo.Rmd
added all sel and q om sim files

```{r runmodels}
if(file.exists(file.path(here(), "misspecification_study", "misspec_demo_fits.RDS"))){
  em_fits <- readRDS(file.path(here(), "misspecification_study", "misspec_demo_fits.RDS"))
} else {
  # run the models
  em_fits = list()
  for(m in 1:8){
    em_fits[[m]] = lapply(1:nsim, function(x){
      out = fit_wham(sim_input[[m]][[x]], 
                     do.osa = FALSE,
                     MakeADFun.silent = TRUE, 
                     retro.silent = TRUE, 
                     save.sdrep = FALSE)
      return(out)
    })
  }
  saveRDS(em_fits, file.path(here(), "misspecification_study", "misspec_demo_fits.RDS"))
}
```

@@

```{r lizretro}
# again had to run this in console because could not get it to knit
#em8lr.dir <- file.path(here(), "misspecification_study", "UR_em4", "liz_retro_plots")
#plot.retro.pars(m=em_fits[[8]][[1]], yr.plot.start=2005, od=em8lr.dir, save.name="UR_em4", 
#  plot.f='png' )
```

>>>>

```{r runmodels}
if(file.exists(file.path(here(), "misspecification_study", "misspec_demo_fits.RDS"))){
  em_fits <- readRDS(file.path(here(), "misspecification_study", "misspec_demo_fits.RDS"))
} else {
  # run the models
  em_fits = list()
  for(m in 1:8){
    em_fits[[m]] = lapply(1:nsim, function(x){
      out = fit_wham(sim_input[[m]][[x]], 
                     do.osa = FALSE,
                     MakeADFun.silent = TRUE, 
                     retro.silent = TRUE, 
                     save.sdrep = TRUE)
      return(out)
    })
  }
  saveRDS(em_fits, file.path(here(), "misspecification_study", "misspec_demo_fits.RDS"))
}
```

@@

```{r lizretro, eval = FALSE}
# again had to run this in console because could not get it to knit
em8lr.dir <- file.path(here(), "misspecification_study", "UR_em4", "liz_retro_plots")
plot.retro.pars(m=em_fits[[8]][[1]], yr.plot.start=2005, od=em8lr.dir, save.name="UR_em4", 
  plot.f='png' )
```
